Covariant Phase Space via MultiSymplectic Geometry

### 2019-03-11 cps-via-ms.tex

\begin{abstract}
In this short talk we present the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
In particular we focus our attention on the construction of the \emph{Covariant Phase Space}, starting from the multi-symplectic approach to geometric classic field theories.
%Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.

>>>>

\begin{abstract}
In this short talk we present part of the results contained in the paper \emph{"Covariant Poisson brackets in geometric field theory"} written by M. Forger and S. V. Romero \cite{forgeromero}.
In particular we focus our attention on the construction of the \emph{Covariant Phase Space}, starting from the multi-symplectic approach to geometric classic field theories.
%Con lo stesso linguaggio si può descrivere più precisamente l'algoritmo di Peierls partendo dalle variazione di soluzioni sottomesse ad una variazione di lagrangiana.
